Graph Exploration and Search

### 2017-11-14 paper.tex
application and future direction

\newcommand{\eat}[1]{}
\newcommand{\stitle}[1]{\vspace{1.6ex}\noindent{\bf #1}}
\newcommand{\eetitle}[1]{\vspace{0.8ex}\noindent{\underline{\em #1}}}
\newcommand{\etitle}[1]{\vspace{0.6ex}\noindent{{\em #1}}}
\newcommand{\ie}{\emph{i.e.,}\xspace}
\newcommand{\NP}{\kw{NP}}
\newcommand{\dist}{\kw{dist}}
\newcommand{\len}{\kw{len}}
\newcommand{\kw}[1]{{\ensuremath {\mathsf{#1}}}}
\newcommand{\MST}{\kw{MST}}
\newcommand{\kws}{\kw{KWS}}
\newcommand{\eg}{\emph{e.g.,}\xspace}
\newcommand{\dnote}[1]{{\color{red}#1}}

@@

@@

>>>>

\newcommand{\eat}[1]{}
\newcommand{\stitle}[1]{\vspace{1.6ex}\noindent{\bf #1}}
\newcommand{\eetitle}[1]{\vspace{0.8ex}\noindent{\underline{\em #1}}}
\newcommand{\etitle}[1]{\vspace{0.6ex}\noindent{{\em #1}}}
\newcommand{\ie}{\emph{i.e.,}\xspace}
\newcommand{\NP}{\kw{NP}}
\newcommand{\dist}{\kw{dist}}
\newcommand{\len}{\kw{len}}
\newcommand{\kw}[1]{{\ensuremath {\mathsf{#1}}}}
\newcommand{\MST}{\kw{MST}\xspace}
\newcommand{\kws}{\kw{KWS}\xspace}
\newcommand{\eg}{\emph{e.g.,}\xspace}
\newcommand{\dnote}[1]{{\color{red}#1}}

@@

The need of graph exploratory is evident in user-friendly 
knowledge exploration~\citep{achiezra2010exploratory},  
 ``why-not'' query processing~\citep{tran2010conquer}, and database security, where highly-correlated 
queries are identified to reverse-engineering 
the sensitive entity information~\citep{tran2014query}.
Another application is interactive sensemaking of complex graph data~\citep{pienta2015scalable}, with broader applications in 
literature search and collaboration recommendation 
in academic networks, attack and anomaly detection  
in cyber networks, and event detection in social media.

@@

The challenges remain open for interactive graph 
exploration. Real-time interactivity is 
crucial to exploration over large graphs. 
This requires scalable graph analytics and 
query suggestion, both are nontrivial for 
graph data. One direction can be to 
integrate emerging scalable graph mining 
and learning methods
to graph exploration tasks, beyond query-based 
exploration. Uncertainty and trustworthiness of 
graph data sources is another challenge 
for exploration tasks, especially for 
knowledge bases. This requires 
truth-aware exploration that guarantees 
the correctness of retrieved information. 
A third direction is to combine 
usable user interfaces and 
scalable graph visualization 
techniques to facilitate 
sensemaking and knowledge discovery 
by graph exploration.
